What do incoming university students believe about open science practices in

### 2021-03-30 analysis/Manuscript.Rmd
calculate correlations

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros
library(psych) #for correlation matrices
library(tidyselect)

@@

 \@ref(tab:chunk-name)

@@

@@

# breadcrumb: I need to use apa_tables.... (in line with papaja)
# pull means & sd into the same column with (sd) in parentheses [done!]
# headings should then be norm, counternorm, difference [done!]

@@

# breadcrumbs: rename the practices so it's easier to read

@@

plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "Critical counternorm", ylab = "Critical norm")
abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))

>>>>

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals

@@

@@

 # \@ref(tab:chunk-name)  [JB removed this from the text above to see if that solves
  # our table caption issue]

@@

# ADD CORRELATIONS (per participant, use df)

critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)

# I'm sure there's a way to automate it, but I can't figure it out...just hard code it
# all_cnorms <- df %>% 
#     select(ends_with("_cnorm"))
#   
# corr <- round(cor(all_), ends_with("_cnorm"),2)))
# 
# 
#   all_norms %>% 
#     cor(ends_with("_norm"), ends_with("_cnorm"))
#   
#  
#   cor(all_norms, method = "pearson") %>% 
#   as.tibble()
# 
# all_correlation <- df %>% 
#     select(c(ends_with("_norm"), ends_with("_cnorm"))) %>% 
#   mutate(item = row.names(.)) %>% 
#   select(item, everything())

# this code works, but I must be able to do this all at once...

# breadcrumbs: when I come back to this, I need to combine these in a tibble
  # and then join it with the existing table...
critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)

hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)

info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)

open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)

open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)

open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)

phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)

preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)

prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)

rbind()

# breadcrumbs: 
# I need to use apa_tables.... (in line with papaja)
# pull means & sd into the same column with (sd) in parentheses [done!]
# headings should then be norm, counternorm, difference [done!]
# add correlations with 95% CIs 
# update practice descriptions so they make sense to readers

@@

@@

plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "critical counternorm", ylab = "critical norm")
abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))
